---
title: "IDM Stats"
author: "Kaysee Arrowsmith"
date: "2024-01-22"
output: html_document
---

# Load Packages and Data

```{r packages, message = F}
library(knitr)
library(tidyverse)
library(glmmTMB)
library(performance)
library(DHARMa)
# library(ENMTools)
# library(predicts)
# library(rJava)
# 
theme_set(theme_light() +
            theme(text = element_text(size = 20)))

gbif <- read_tsv("gbif-top5.csv") %>%
  filter(year >= 2018)

bbna <- read.csv("bbna_pnwbba.csv", stringsAsFactors = F)
```

# Completed Evals
Load up completed evaluation metrics.

```{r load evals, message = F}
# Bifarius
bifcham.evaldf <- read.csv("completed-evals/bifcham-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "bifcham")
bifcham.thresholddf <- read.csv("completed-evals/bifcham-threshold.csv", stringsAsFactors = F) %>%
  mutate(X = "bifcham")

bifcir.evaldf <- read.csv("completed-evals/bifcir-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "bifcir")
bifcir.thresholddf <- read.csv("completed-evals/bifcir-threshold.csv", stringsAsFactors = F) %>%
  mutate(X = "bifcir")

biflup.evaldf <- read.csv("completed-evals/biflup-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "biflup")
biflup.thresholddf <- read.csv("completed-evals/biflup-threshold.csv", stringsAsFactors = F) %>%
  mutate(X = "biflup")

bifpen.evaldf <- read.csv("completed-evals/bifpen-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "bifpen")
bifpen.thresholddf <- read.csv("completed-evals/bifpen-threshold.csv", stringsAsFactors = F) %>%
  mutate(X = "bifpen")

bifrub.evaldf <- read.csv("completed-evals/bifrub-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "bifrub")
bifrub.thresholddf <- read.csv("completed-evals/bifrub-threshold.csv", stringsAsFactors = F) %>%
  mutate(X = "bifrub")


# Flavifrons
flavcham.evaldf <- read.csv("completed-evals/flavcham-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "flavcham")
flavcham.thresholddf <- read.csv("completed-evals/flavcham-threshold.csv", stringsAsFactors = F) %>%
  mutate(X = "flavcham")

flavcir.evaldf <- read.csv("completed-evals/flavcir-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "flavcir")
flavcir.thresholddf <- read.csv("completed-evals/flavcir-threshold.csv", stringsAsFactors = F) %>%
  mutate(X = "flavcir")

flavlup.evaldf <- read.csv("completed-evals/flavlup-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "flavlup")
flavlup.thresholddf <- read.csv("completed-evals/flavlup-threshold.csv", stringsAsFactors = F) %>%
  mutate(X = "flavlup")

flavpen.evaldf <- read.csv("completed-evals/flavpen-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "flavpen")
flavpen.thresholddf <- read.csv("completed-evals/flavpen-threshold.csv", stringsAsFactors = F) %>%
  mutate(X = "flavpen")

flavrub.evaldf <- read.csv("completed-evals/flavrub-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "flavrub")
flavrub.thresholddf <- read.csv("completed-evals/flavrub-threshold.csv", stringsAsFactors = F) %>%
  mutate(X = "flavrub")

# Mixtus
mixcham.evaldf <- read.csv("completed-evals/mixcham-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "mixcham")
mixcham.thresholddf <- read.csv("completed-evals/mixcham-threshold.csv", stringsAsFactors = F) %>%
  mutate(X = "mixcham")

mixcir.evaldf <- read.csv("completed-evals/mixcir-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "mixcir")
mixcir.thresholddf <- read.csv("completed-evals/mixcir-threshold.csv", stringsAsFactors = F) %>%
  mutate(X = "mixcir")

mixlup.evaldf <- read.csv("completed-evals/mixlup-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "mixlup")
mixlup.thresholddf <- read.csv("completed-evals/mixlup-threshold.csv", stringsAsFactors = F) %>%
  mutate(X = "mixlup")

mixpen.evaldf <- read.csv("completed-evals/mixpen-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "mixpen")
mixpen.thresholddf <- read.csv("completed-evals/mixpen-threshold.csv", stringsAsFactors = F) %>%
  mutate(X = "mixpen")

mixrub.evaldf <- read.csv("completed-evals/mixrub-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "mixrub")
mixrub.thresholddf <- read.csv("completed-evals/mixrub-threshold.csv", stringsAsFactors = F) %>%
  mutate(X = "mixrub")

#Vosnesenskii
voscham.evaldf <- read.csv("completed-evals/voscham-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "voscham")
voscham.thresholddf <- read.csv("completed-evals/voscham-threshold.csv", stringsAsFactors = F) %>%
  mutate(X = "voscham")

voscir.evaldf <- read.csv("completed-evals/voscir-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "voscir")
voscir.thresholddf <- read.csv("completed-evals/voscir-threshold.csv", stringsAsFactors = F) %>%
  mutate(X = "voscir")

voslup.evaldf <- read.csv("completed-evals/voslup-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "voslup")
voslup.thresholddf <- read.csv("completed-evals/voslup-threshold.csv", stringsAsFactors = F) %>%
  mutate(X = "voslup")

vospen.evaldf <- read.csv("completed-evals/vospen-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "vospen")
vospen.thresholddf <- read.csv("completed-evals/vospen-threshold.csv", stringsAsFactors = F) %>%
  mutate(X = "vospen")

vosrub.evaldf <- read.csv("completed-evals/vosrub-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "vosrub")
vosrub.thresholddf <- read.csv("completed-evals/vosrub-threshold.csv", stringsAsFactors = F) %>%
  mutate(X = "vosrub")

# All runs
area.allruns <- read.csv("thresh-areas-all.csv")
```


# Create dataframe
Create a dataframe of all interaction pairings.

```{r int df}
# Make some working dataframes
all.evals <- bind_rows(bifcham.evaldf, bifcir.evaldf, biflup.evaldf, bifpen.evaldf, bifrub.evaldf, flavcham.evaldf, flavcir.evaldf, flavlup.evaldf, flavpen.evaldf, flavrub.evaldf, mixcham.evaldf, mixcir.evaldf, mixlup.evaldf, mixpen.evaldf, mixrub.evaldf, 
                       voscham.evaldf, voscir.evaldf, voslup.evaldf, vospen.evaldf, vosrub.evaldf)

# write.csv(all.evals, "all-evals.csv")

int.df <- data.frame(int = NA,
                     bee_species = NA, # bifarius, flavifrons, mixtus, vosnesenskii
                     plant_genus = NA, # Chamaenerion, Cirsium, Lupinus, Penstemon, Rubus
                     model_run = NA, # range from 1-100 for each interaction
                     delta_AUC = NA, # IDM - overlap
                     delta_TSS = NA, # IDM - overlap
                     RMSE = NA)

ints <- sort(unique(all.evals$X))

for(i in 1:length(ints)){
  int = ints[i]
  for(j in 1:100){
    df = all.evals %>%
      filter(X == int,
             run == j)
    delta_AUC = (df %>% filter(model == "IDM"))$AUC - (df %>% filter(model == "overlap"))$AUC
    delta_TSS = (df %>% filter(model == "IDM"))$TSS - (df %>% filter(model == "overlap"))$TSS
    RMSE = (df %>% filter(model == "overlap"))$RMSE
    
    temp.df = data.frame(int = int,
                         bee_species = NA,
                         plant_genus = NA,
                         model_run = j,
                         delta_AUC = delta_AUC,
                         delta_TSS = delta_TSS,
                         RMSE = RMSE)
    int.df = bind_rows(int.df, temp.df)
  }
}

# Some bee and plant info
plant.info <- gbif %>%
  group_by(genus) %>%
  tally(name = "n_plant_records") %>% # number of records of this plant in GBIF
  left_join(gbif, by = "genus") %>%
  filter(!is.na(species)) %>%
  group_by(genus, n_plant_records) %>%
  summarise(n_plant_species = length(unique(species))) # number of species of this genus in GBIF

bee.info <- bbna %>%
  group_by(species) %>%
  tally(name = "n_bee_records") %>% # number of records of this bee in BBNA
  left_join(bbna, by = "species") %>%
  group_by(species, plant.host.genus, n_bee_records) %>%
  tally(name = "n_int") %>% # number of records of this interaction in PNWBBA
  mutate(relabund_int = n_int/n_bee_records) # relative abundance of this interaction among species' total

# Fill in bee and plant info
int.df <- int.df %>%
  mutate(bee_species = ifelse(str_detect(int, "^bif"), "bifarius",
                              ifelse(str_detect(int, "^flav"), "flavifrons",
                                     ifelse(str_detect(int, "^mix"), "mixtus", 
                                            "vosnesenskii"))),
         plant_genus = ifelse(str_detect(int, "cham"), "Chamaenerion", 
                              ifelse(str_detect(int, "cir"), "Cirsium",
                                     ifelse(str_detect(int, "lup"), "Lupinus",
                                            ifelse(str_detect(int, "pen"), "Penstemon",
                                                   "Rubus"))))) %>%
  left_join(plant.info, by = c("plant_genus" = "genus")) %>%
  left_join(bee.info, by = c("bee_species" = "species", "plant_genus" = "plant.host.genus"))
```

# Stats
## RMSE
```{r rmse}
mean(all.evals$RMSE, na.rm = T)
sd(all.evals$RMSE, na.rm = T)

rmse.bif <- ggplot(int.df %>% filter(bee_species == "bifarius"), aes(x = plant_genus, y = RMSE)) +
  geom_boxplot() +
  coord_cartesian(ylim = c(0, 0.25)) +
  theme(axis.text.x = element_text(angle = 55, hjust=1),
        axis.title = element_blank())
ggsave("figures/bif-rmse.png", rmse.bif, width = 3.5, height = 6.5, units = "in")

rmse.flav <- ggplot(int.df %>% filter(bee_species == "flavifrons"), aes(x = plant_genus, y = RMSE)) +
  geom_boxplot() +
  coord_cartesian(ylim = c(0, 0.25)) +
  theme(axis.text.x = element_text(angle = 55, hjust=1),
        axis.title = element_blank())
ggsave("figures/flav-rmse.png", rmse.flav, width = 3.5, height = 6.5, units = "in")

rmse.mix <- ggplot(int.df %>% filter(bee_species == "mixtus"), aes(x = plant_genus, y = RMSE)) +
  geom_boxplot() +
  coord_cartesian(ylim = c(0, 0.25)) +
  theme(axis.text.x = element_text(angle = 55, hjust=1),
        axis.title = element_blank())
ggsave("figures/mix-rmse.png", rmse.mix, width = 3.5, height = 6.5, units = "in")


rmse.vos <- ggplot(int.df %>% filter(bee_species == "vosnesenskii"), aes(x = plant_genus, y = RMSE)) +
  geom_boxplot() +
  coord_cartesian(ylim = c(0, 0.25)) +
  theme(axis.text.x = element_text(angle = 55, hjust=1),
        axis.title = element_blank())
ggsave("figures/vos-rmse.png", rmse.vos, width = 3.5, height = 6.5, units = "in")
```

## Thresholds
```{r thresh stats}
allints.thresholddf <- bind_rows(bifcham.thresholddf, bifcir.thresholddf, biflup.thresholddf, bifpen.thresholddf, bifrub.thresholddf, flavcham.thresholddf, flavcir.thresholddf, flavlup.thresholddf, flavpen.thresholddf, flavrub.thresholddf, mixcham.thresholddf, mixcir.thresholddf, mixlup.thresholddf, mixpen.thresholddf, mixrub.thresholddf, 
                              voscham.thresholddf, voscir.thresholddf, voslup.thresholddf, vospen.thresholddf, vosrub.thresholddf) %>%
  mutate(total_cells = n_shared + n_IDM + n_overlap) %>%
  left_join(int.df %>% group_by(int) %>% summarise(bee_species = unique(bee_species), plant_genus = unique(plant_genus)), by = c("X" = "int"))

mean(allints.thresholddf$prop.shared)
sd.shared = sd(allints.thresholddf$prop.shared)
max(allints.thresholddf$prop.shared)

mean(allints.thresholddf$prop.idm)
sd.idm = sd(allints.thresholddf$prop.idm)

mean(allints.thresholddf$prop.overlap)
sd.overlap = sd(allints.thresholddf$prop.overlap)

thresh.sds <- allints.thresholddf %>%
  group_by(X) %>%
  summarise(sd.shared = sd(prop.shared),
            sd.overlap = sd(prop.overlap),
            sd.idm = sd(prop.idm))

thresh.long <- allints.thresholddf %>%
  group_by(X, bee_species, plant_genus) %>%
  summarise(mean.shared = mean(prop.shared), 
            mean.idm = mean(prop.idm),
            mean.overlap = mean(prop.overlap)) %>%
  left_join(thresh.sds, by = "X") %>%
  mutate(sdmax.shared = mean.shared + sd.shared,
         sdmin.shared = mean.shared - sd.shared,
        sdmax.overlap = mean.shared + mean.overlap + sd.overlap,
        sdmin.overlap = mean.shared + mean.overlap - sd.overlap,
        sdmax.idm = mean.idm ) %>%
  pivot_longer(cols = c(mean.shared, mean.idm, mean.overlap),
               names_to = "type",
               values_to = "value") %>%
  left_join(data.frame(X = sort(unique(allints.thresholddf$X)),
                       org = c(1:20)), by = "X")

thresh.plot <- ggplot(thresh.long, aes(x = reorder(X, desc(org)), y = value, fill = type)) +
  geom_bar(stat = "identity",
           position = "stack") +
  geom_errorbar(aes(ymin = sdmin.shared,
                    ymax = sdmax.shared),
                
                    col = "#7e7f60",
                width = 0.3) +
  coord_flip() +
  labs(x = "Interaction", y = "Proportion of Raster Cells", fill = "Model Type") +
  scale_fill_manual(values = c("#f1605d",
                               "#721f81",
                               "#fcfdbf"),
                    labels = c("IDM", # mean.idm
                               "Overlap", # mean.overlap
                               "Overlap & IDM")) # mean.shared
thresh.plot
ggsave("figures/threshold-stats.png", plot = thresh.plot, width = 8, height = 6, units = "in")

area.allruns <- area.allruns %>%
  left_join(int.df, by = c("int", c("run" = "model_run")))

thresh.idmarea <- aov(idm ~ bee_species + plant_genus, data = area.allruns)
thresh.idmposthoc <- TukeyHSD(thresh.idmarea)

thresh.overlaparea <- aov(overlap ~ bee_species + plant_genus, data = area.allruns)
thresh.overlapposthoc <- TukeyHSD(thresh.overlaparea)

```




## Absolute Model Performance
### Bifarius
#### Chamaenerion
```{r bifcham eval plots}
# AUC
bifcham.auctest <- aov(AUC ~ model, data = bifcham.evaldf)
summary(bifcham.auctest)

bifcham.aucplot <- ggplot(bifcham.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.7, 1.03))
bifcham.aucplot
ggsave("figures/bifcham-auc.png", bifcham.aucplot, width = 2.5, height = 4, units = "in")

# TSS
bifcham.tsstest <- aov(TSS ~ model, data = bifcham.evaldf)
summary(bifcham.tsstest)

bifcham.tssplot <- ggplot(bifcham.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.4, 1.03))
bifcham.tssplot
ggsave("figures/bifcham-tss.png", bifcham.tssplot, width = 2.5, height = 4, units = "in")

# RMSE
bifcham.rmsetest <- t.test(bifcham.evaldf$RMSE)
bifcham.rmsetest
```


#### Cirsium
```{r bifcir eval plots}
# AUC
bifcir.auctest <- aov(AUC ~ model, data = bifcir.evaldf)
summary(bifcir.auctest)

bifcir.aucplot <- ggplot(bifcir.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.7, 1.03))
bifcir.aucplot
ggsave("figures/bifcir-auc.png", bifcir.aucplot, width = 2.5, height = 4, units = "in")

# TSS
bifcir.tsstest <- aov(TSS ~ model, data = bifcir.evaldf)
summary(bifcir.tsstest)

bifcir.tssplot <- ggplot(bifcir.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.4, 1.03))
bifcir.tssplot
ggsave("figures/bifcir-tss.png", bifcir.tssplot, width = 2.5, height = 4, units = "in")

# RMSE
bifcir.rmsetest <- t.test(bifcir.evaldf$RMSE)
bifcir.rmsetest
```


#### Lupinus

```{r biflup eval plots}
# AUC
biflup.auctest <- aov(AUC ~ model, data = biflup.evaldf)
summary(biflup.auctest)

biflup.aucplot <- ggplot(biflup.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.7, 1.03))
biflup.aucplot
ggsave("figures/biflup-auc.png", biflup.aucplot, width = 2.5, height = 4, units = "in")

# TSS
biflup.tsstest <- aov(TSS ~ model, data = biflup.evaldf)
summary(biflup.tsstest)

biflup.tssplot <- ggplot(biflup.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.4, 1.03))
biflup.tssplot
ggsave("figures/biflup-tss.png", biflup.tssplot, width = 2.5, height = 4, units = "in")

# RMSE
biflup.rmsetest <- t.test(biflup.evaldf$RMSE)
biflup.rmsetest
```


#### Penstemon
```{r bifpen eval plots}
# AUC
bifpen.auctest <- aov(AUC ~ model, data = bifpen.evaldf)
summary(bifpen.auctest)

bifpen.aucplot <- ggplot(bifpen.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot()  +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.7, 1.03))
bifpen.aucplot
ggsave("figures/bifpen-auc.png", bifpen.aucplot, width = 2.5, height = 4, units = "in")


# TSS
bifpen.tsstest <- aov(TSS ~ model, data = bifpen.evaldf)
summary(bifpen.tsstest)

bifpen.tssplot <- ggplot(bifpen.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.4, 1.03))
bifpen.tssplot
ggsave("figures/bifpen-tss.png", bifpen.tssplot, width = 2.5, height = 4, units = "in")

# RMSE
bifpen.rmsetest <- t.test(bifpen.evaldf$RMSE)
bifpen.rmsetest
```


#### Rubus
```{r bifrub eval plots}
# AUC
bifrub.auctest <- aov(AUC ~ model, data = bifrub.evaldf)
summary(bifrub.auctest)

bifrub.aucplot <- ggplot(bifrub.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot()  +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.7, 1.03))
bifrub.aucplot
ggsave("figures/bifrub-auc.png", bifrub.aucplot, width = 2.5, height = 4, units = "in")


# TSS
bifrub.tsstest <- aov(TSS ~ model, data = bifrub.evaldf)
summary(bifrub.tsstest)

bifrub.tssplot <- ggplot(bifrub.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.4, 1.03))
bifrub.tssplot
ggsave("figures/bifrub-tss.png", bifrub.tssplot, width = 2.5, height = 4, units = "in")

# RMSE
bifrub.rmsetest <- t.test(bifrub.evaldf$RMSE)
bifrub.rmsetest
```

### Flavifrons
#### Chamaenerion
```{r flavcham eval plots}
# AUC
flavcham.auctest <- aov(AUC ~ model, data = flavcham.evaldf)
summary(flavcham.auctest)

flavcham.aucplot <- ggplot(flavcham.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.7, 1.03))
flavcham.aucplot
ggsave("figures/flavcham-auc.png", flavcham.aucplot, width = 2.5, height = 4, units = "in")

# TSS
flavcham.tsstest <- aov(TSS ~ model, data = flavcham.evaldf)
summary(flavcham.tsstest)

flavcham.tssplot <- ggplot(flavcham.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.4, 1.03))
flavcham.tssplot
ggsave("figures/flavcham-tss.png", flavcham.tssplot, width = 2.5, height = 4, units = "in")

# RMSE
flavcham.rmsetest <- t.test(flavcham.evaldf$RMSE)
flavcham.rmsetest
```


#### Cirsium
```{r flavcir eval plots}
# AUC
flavcir.auctest <- aov(AUC ~ model, data = flavcir.evaldf)
summary(flavcir.auctest)

flavcir.aucplot <- ggplot(flavcir.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.7, 1.03))
flavcir.aucplot
ggsave("figures/flavcir-auc.png", flavcir.aucplot, width = 2.5, height = 4, units = "in")

# TSS
flavcir.tsstest <- aov(TSS ~ model, data = flavcir.evaldf)
summary(flavcir.tsstest)

flavcir.tssplot <- ggplot(flavcir.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.4, 1.03))
flavcir.tssplot
ggsave("figures/flavcir-tss.png", flavcir.tssplot, width = 2.5, height = 4, units = "in")

# RMSE
flavcir.rmsetest <- t.test(flavcir.evaldf$RMSE)
flavcir.rmsetest
```


#### Lupinus
```{r flavlup eval plots}
# AUC
flavlup.auctest <- aov(AUC ~ model, data = flavlup.evaldf)
summary(flavlup.auctest)

flavlup.aucplot <- ggplot(flavlup.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.7, 1.03))
flavlup.aucplot
ggsave("figures/flavlup-auc.png", flavlup.aucplot, width = 2.5, height = 4, units = "in")

# TSS
flavlup.tsstest <- aov(TSS ~ model, data = flavlup.evaldf)
summary(flavlup.tsstest)

flavlup.tssplot <- ggplot(flavlup.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.4, 1.03))
flavlup.tssplot
ggsave("figures/flavlup-tss.png", flavlup.tssplot, width = 2.5, height = 4, units = "in")

# RMSE
flavlup.rmsetest <- t.test(flavlup.evaldf$RMSE)
flavlup.rmsetest
```


#### Penstemon
```{r flavpen eval plots}
# AUC
flavpen.auctest <- aov(AUC ~ model, data = flavpen.evaldf)
summary(flavpen.auctest)

flavpen.aucplot <- ggplot(flavpen.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.7, 1.03))
flavpen.aucplot
ggsave("figures/flavpen-auc.png", flavpen.aucplot, width = 2.5, height = 4, units = "in")

# TSS
flavpen.tsstest <- aov(TSS ~ model, data = flavpen.evaldf)
summary(flavpen.tsstest)

flavpen.tssplot <- ggplot(flavpen.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.4, 1.03))
flavpen.tssplot
ggsave("figures/flavpen-tss.png", flavpen.tssplot, width = 2.5, height = 4, units = "in")

# RMSE
flavpen.rmsetest <- t.test(flavpen.evaldf$RMSE)
flavpen.rmsetest
```

#### Rubus
```{r flavrub eval plots}
# AUC
flavrub.auctest <- aov(AUC ~ model, data = flavrub.evaldf)
summary(flavrub.auctest)

flavrub.aucplot <- ggplot(flavrub.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.7, 1.03))
flavrub.aucplot
ggsave("figures/flavrub-auc.png", flavrub.aucplot, width = 2.5, height = 4, units = "in")

# TSS
flavrub.tsstest <- aov(TSS ~ model, data = flavrub.evaldf)
summary(flavrub.tsstest)

flavrub.tssplot <- ggplot(flavrub.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.4, 1.03))
flavrub.tssplot
ggsave("figures/flavrub-tss.png", flavrub.tssplot, width = 2.5, height = 4, units = "in")

# RMSE
flavrub.rmsetest <- t.test(flavrub.evaldf$RMSE)
flavrub.rmsetest
```

### Mixtus
#### Chamaenerion
```{r mixcham eval plots}
# AUC
mixcham.auctest <- aov(AUC ~ model, data = mixcham.evaldf)
summary(mixcham.auctest)

mixcham.aucplot <- ggplot(mixcham.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.7, 1.03))
mixcham.aucplot
ggsave("figures/mixcham-auc.png", mixcham.aucplot, width = 2.5, height = 4, units = "in")

# TSS
mixcham.tsstest <- aov(TSS ~ model, data = mixcham.evaldf)
summary(mixcham.tsstest)

mixcham.tssplot <- ggplot(mixcham.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.4, 1.03))
mixcham.tssplot
ggsave("figures/mixcham-tss.png", mixcham.tssplot, width = 2.5, height = 4, units = "in")

# RMSE
mixcham.rmsetest <- t.test(mixcham.evaldf$RMSE)
mixcham.rmsetest
```


#### Cirsium
```{r mixcir eval plots}
# AUC
mixcir.auctest <- aov(AUC ~ model, data = mixcir.evaldf)
summary(mixcir.auctest)

mixcir.aucplot <- ggplot(mixcir.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.7, 1.03))
mixcir.aucplot
ggsave("figures/mixcir-auc.png", mixcir.aucplot, width = 2.5, height = 4, units = "in")

# TSS
mixcir.tsstest <- aov(TSS ~ model, data = mixcir.evaldf)
summary(mixcir.tsstest)

mixcir.tssplot <- ggplot(mixcir.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.4, 1.03))
mixcir.tssplot
ggsave("figures/mixcir-tss.png", mixcir.tssplot, width = 2.5, height = 4, units = "in")

# RMSE
mixcir.rmsetest <- t.test(mixcir.evaldf$RMSE)
mixcir.rmsetest
```


#### Lupinus
```{r mixlup eval plots}
# AUC
mixlup.auctest <- aov(AUC ~ model, data = mixlup.evaldf)
summary(mixlup.auctest)

mixlup.aucplot <- ggplot(mixlup.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.7, 1.03))
mixlup.aucplot
ggsave("figures/mixlup-auc.png", mixlup.aucplot, width = 2.5, height = 4, units = "in")

# TSS
mixlup.tsstest <- aov(TSS ~ model, data = mixlup.evaldf)
summary(mixlup.tsstest)

mixlup.tssplot <- ggplot(mixlup.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.4, 1.03))
mixlup.tssplot
ggsave("figures/mixlup-tss.png", mixlup.tssplot, width = 2.5, height = 4, units = "in")

# RMSE
mixlup.rmsetest <- t.test(mixlup.evaldf$RMSE)
mixlup.rmsetest
```


#### Penstemon
```{r mixpen eval plots}
# AUC
mixpen.auctest <- aov(AUC ~ model, data = mixpen.evaldf)
summary(mixpen.auctest)

mixpen.aucplot <- ggplot(mixpen.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.7, 1.03))
mixpen.aucplot
ggsave("figures/mixpen-auc.png", mixpen.aucplot, width = 2.5, height = 4, units = "in")

# TSS
mixpen.tsstest <- aov(TSS ~ model, data = mixpen.evaldf)
summary(mixpen.tsstest)

mixpen.tssplot <- ggplot(mixpen.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.4, 1.03))
mixpen.tssplot
ggsave("figures/mixpen-tss.png", mixpen.tssplot, width = 2.5, height = 4, units = "in")

# RMSE
mixpen.rmsetest <- t.test(mixpen.evaldf$RMSE)
mixpen.rmsetest
```


#### Rubus
```{r mixrub eval plots}
# AUC
mixrub.auctest <- aov(AUC ~ model, data = mixrub.evaldf)
summary(mixrub.auctest)

mixrub.aucplot <- ggplot(mixrub.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.7, 1.03))
mixrub.aucplot
ggsave("figures/mixrub-auc.png", mixrub.aucplot, width = 2.5, height = 4, units = "in")

# TSS
mixrub.tsstest <- aov(TSS ~ model, data = mixrub.evaldf)
summary(mixrub.tsstest)

mixrub.tssplot <- ggplot(mixrub.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.4, 1.03))
mixrub.tssplot
ggsave("figures/mixrub-tss.png", mixrub.tssplot, width = 2.5, height = 4, units = "in")

# RMSE
mixrub.rmsetest <- t.test(mixrub.evaldf$RMSE)
mixrub.rmsetest
```


### Vosnesenskii
#### Chamaenerion
```{r voscham eval plots}
# AUC
voscham.auctest <- aov(AUC ~ model, data = voscham.evaldf)
summary(voscham.auctest)

voscham.aucplot <- ggplot(voscham.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.7, 1.03))
voscham.aucplot
ggsave("figures/voscham-auc.png", voscham.aucplot, width = 2.5, height = 4, units = "in")

# TSS
voscham.tsstest <- aov(TSS ~ model, data = voscham.evaldf)
summary(voscham.tsstest)

voscham.tssplot <- ggplot(voscham.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.4, 1.03))
voscham.tssplot
ggsave("figures/voscham-tss.png", voscham.tssplot, width = 2.5, height = 4, units = "in")

# RMSE
voscham.rmsetest <- t.test(voscham.evaldf$RMSE)
voscham.rmsetest
```

#### Cirsium
```{r voscir eval plots}
# AUC
voscir.auctest <- aov(AUC ~ model, data = voscir.evaldf)
summary(voscir.auctest)

voscir.aucplot <- ggplot(voscir.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
 theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.7, 1.03))
voscir.aucplot
ggsave("figures/voscir-auc.png", voscir.aucplot, width = 2.5, height = 4, units = "in")

# TSS
voscir.tsstest <- aov(TSS ~ model, data = voscir.evaldf)
summary(voscir.tsstest)

voscir.tssplot <- ggplot(voscir.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.4, 1.03))
voscir.tssplot
ggsave("figures/voscir-tss.png", voscir.tssplot, width = 2.5, height = 4, units = "in")

# RMSE
voscir.rmsetest <- t.test(voscir.evaldf$RMSE)
voscir.rmsetest
```

#### Lupinus
```{r voslup eval plots}
# AUC
voslup.auctest <- aov(AUC ~ model, data = voslup.evaldf)
summary(voslup.auctest)

voslup.aucplot <- ggplot(voslup.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.7, 1.03))
voslup.aucplot
ggsave("figures/voslup-auc.png", voslup.aucplot, width = 2.5, height = 4, units = "in")

# TSS
voslup.tsstest <- aov(TSS ~ model, data = voslup.evaldf)
summary(voslup.tsstest)

voslup.tssplot <- ggplot(voslup.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.4, 1.03))
voslup.tssplot
ggsave("figures/voslup-tss.png", voslup.tssplot, width = 2.5, height = 4, units = "in")

# RMSE
voslup.rmsetest <- t.test(voslup.evaldf$RMSE)
voslup.rmsetest
```

#### Penstemon
```{r vospen eval plots}
# AUC
vospen.auctest <- aov(AUC ~ model, data = vospen.evaldf)
summary(vospen.auctest)

vospen.aucplot <- ggplot(vospen.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.7, 1.03))
vospen.aucplot
ggsave("figures/vospen-auc.png", vospen.aucplot, width = 2.5, height = 4, units = "in")

# TSS
vospen.tsstest <- aov(TSS ~ model, data = vospen.evaldf)
summary(vospen.tsstest)

vospen.tssplot <- ggplot(vospen.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.4, 1.03))
vospen.tssplot
ggsave("figures/vospen-tss.png", vospen.tssplot, width = 2.5, height = 4, units = "in")

# RMSE
vospen.rmsetest <- t.test(vospen.evaldf$RMSE)
vospen.rmsetest
```

#### Rubus
```{r vosrub eval plots}
# AUC
vosrub.auctest <- aov(AUC ~ model, data = vosrub.evaldf)
summary(vosrub.auctest)

vosrub.aucplot <- ggplot(vosrub.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.7, 1.03))
vosrub.aucplot
ggsave("figures/vosrub-auc.png", vosrub.aucplot, width = 2.5, height = 4, units = "in")

# TSS
vosrub.tsstest <- aov(TSS ~ model, data = vosrub.evaldf)
summary(vosrub.tsstest)

vosrub.tssplot <- ggplot(vosrub.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("overlap", "IDM"),
                   labels = c("Overlap", "IDM")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.4, 1.03))
vosrub.tssplot
ggsave("figures/vosrub-tss.png", vosrub.tssplot, width = 2.5, height = 4, units = "in")

# RMSE
vosrub.rmsetest <- t.test(vosrub.evaldf$RMSE)
vosrub.rmsetest
```



<!-- ##### R. spectabilis -->
<!-- ```{r mix rspec} -->
<!-- vosrubspec.evaldf <- vosrubspec.evaldf %>% -->
<!--   bind_rows(vosrub.evaldf %>% -->
<!--               filter(model == "IDM")) -->

<!-- # AUC -->
<!-- vosrubspec.auctest <- aov(AUC ~ model, data = vosrubspec.evaldf) -->
<!-- summary(vosrubspec.auctest) -->
<!-- TukeyHSD(vosrubspec.auctest) -->

<!-- vosrubspec.aucplot <- ggplot(vosrubspec.evaldf, aes(x = model, y = AUC)) + -->
<!--   geom_boxplot() + -->
<!--   scale_x_discrete(limit = c("vbrubspec", "rubspecbv", "IDM"), -->
<!--                    labels = c("Plant First", "Bee First", "Interaction")) + -->
<!--   theme(axis.text.x = element_blank(), -->
<!--         axis.title = element_blank()) + -->
<!--   lims(y = c(0.7, 1.03)) -->
<!-- vosrubspec.aucplot -->
<!-- ggsave("figures/vosrubspec-auc.png", vosrubspec.aucplot, width = 2.5, height = 4, units = "in") -->

<!-- # TSS -->
<!-- vosrubspec.tsstest <- aov(TSS ~ model, data = vosrubspec.evaldf) -->
<!-- summary(vosrubspec.tsstest) -->
<!-- TukeyHSD(vosrubspec.tsstest) -->

<!-- vosrubspec.tssplot <- ggplot(vosrubspec.evaldf, aes(x = model, y = TSS)) +  -->
<!--   geom_boxplot() + -->
<!--   scale_x_discrete(limit = c("vbrubspec", "rubspecbv", "IDM"), -->
<!--                    labels = c("Plant First", "Bee First", "Interaction")) + -->
<!--   theme(axis.text.x = element_blank(), -->
<!--         axis.title = element_blank()) + -->
<!--   lims(y = c(0.4, 1.03)) -->
<!-- vosrubspec.tssplot -->
<!-- ggsave("figures/vosrubspec-tss.png", vosrubspec.tssplot, width = 2.5, height = 4, units = "in") -->
<!-- ``` -->

<!-- ##### R. parviflorus -->
<!-- ```{r vos rparv} -->
<!-- vosrubparv.evaldf <- vosrubparv.evaldf %>% -->
<!--   bind_rows(vosrub.evaldf %>% -->
<!--               filter(model == "IDM")) -->

<!-- # AUC -->
<!-- vosrubparv.auctest <- aov(AUC ~ model, data = vosrubparv.evaldf) -->
<!-- summary(vosrubparv.auctest) -->
<!-- TukeyHSD(vosrubparv.auctest) -->

<!-- vosrubparv.aucplot <- ggplot(vosrubparv.evaldf, aes(x = model, y = AUC)) + -->
<!--   geom_boxplot() + -->
<!--   scale_x_discrete(limit = c("vbrubparv", "rubparvbv", "IDM"), -->
<!--                    labels = c("Plant First", "Bee First", "Interaction")) + -->
<!--   theme(axis.text.x = element_blank(), -->
<!--         axis.title = element_blank()) + -->
<!--   lims(y = c(0.7, 1.03)) -->
<!-- vosrubparv.aucplot -->
<!-- ggsave("figures/vosrubparv-auc.png", vosrubparv.aucplot, width = 2.5, height = 4, units = "in") -->

<!-- # TSS -->
<!-- vosrubparv.tsstest <- aov(TSS ~ model, data = vosrubparv.evaldf) -->
<!-- summary(vosrubparv.tsstest) -->
<!-- TukeyHSD(vosrubparv.tsstest) -->

<!-- vosrubparv.tssplot <- ggplot(vosrubparv.evaldf, aes(x = model, y = TSS)) +  -->
<!--   geom_boxplot() + -->
<!--   scale_x_discrete(limit = c("vbrubparv", "rubparvbv", "IDM"), -->
<!--                    labels = c("Plant First", "Bee First", "Interaction")) + -->
<!--   theme(axis.text.x = element_blank(), -->
<!--         axis.title = element_blank()) + -->
<!--   lims(y = c(0.4, 1.03)) -->
<!-- vosrubparv.tssplot -->
<!-- ggsave("figures/vosrubparv-tss.png", vosrubparv.tssplot, width = 2.5, height = 4, units = "in") -->
<!-- ``` -->

## Relative Difference in Model Performance

Here, we want to see how we can determine whether an IDM would be better than an overlap model for a particular interaction.

*AUC*: 

```{r relative stats}
auc.test <- glmmTMB(delta_AUC ~ relabund_int + n_plant_records + n_bee_records + (1|bee_species) + (1|plant_genus), data = int.df, family = gaussian)
check_collinearity(auc.test)
check_overdispersion(auc.test)
plot(simulateResiduals(auc.test))
summary(auc.test)

tss.test <- glmmTMB(delta_TSS ~ relabund_int + n_plant_records + n_bee_records + (1|bee_species) + (1|plant_genus), data = int.df, family = gaussian)
check_collinearity(tss.test)
check_overdispersion(tss.test)
plot(simulateResiduals(tss.test))
summary(tss.test)

rmse.test <- glmmTMB(RMSE ~ relabund_int + n_plant_records + n_bee_records + (1|bee_species) + (1|plant_genus), data = int.df, family = lognormal)
check_collinearity(rmse.test)
check_overdispersion(rmse.test)
plot(simulateResiduals(rmse.test))
summary(rmse.test)
```

There seems to be a pretty clear story here. Though the DHARMa plots aren't great.

# Summary Stats
```{r summar}
bee.info2 <- bee.info %>%
  filter(species %in% c("bifarius", "flavifrons", "mixtus", "vosnesenskii"),
         plant.host.genus %in% c("Chamaenerion", "Cirsium", "Lupinus", "Penstemon", "Rubus"))

mean(bee.info2$relabund_int)
sd(bee.info2$relabund_int)
```

