---
title: "IDM Stats"
author: "Kaysee Arrowsmith"
date: "2024-01-22"
output: html_document
---

# Load Packages and Data

```{r packages, message = F}
library(knitr)
library(tidyverse)
library(glmmTMB)
# library(ENMTools)
# library(predicts)
# library(rJava)
# 
# theme_set(theme_light() +
#             theme(text = element_text(size = 20)))

gbif <- read_tsv("gbif-top5.csv") %>%
  filter(year >= 2018)

bbna <- read.csv("bbna_pnwbba.csv", stringsAsFactors = F)
```

# Completed Evals
Load up completed evaluation metrics.

```{r load evals, message = F}
# Bifarius
bifcham.evaldf <- read.csv("completed-evals/bifcham-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "bifcham")
bifcham.varimpdf <- read.csv("completed-evals/bifcham-varimport.csv", stringsAsFactors = F)

bifcir.evaldf <- read.csv("completed-evals/bifcir-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "bifcir")
bifcir.varimpdf <- read.csv("completed-evals/bifcir-varimport.csv", stringsAsFactors = F)

biflup.evaldf <- read.csv("completed-evals/biflup-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "biflup")
biflup.varimpdf <- read.csv("completed-evals/biflup-varimport.csv", stringsAsFactors = F)

bifpen.evaldf <- read.csv("completed-evals/bifpen-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "bifpen")
bifpen.varimpdf <- read.csv("completed-evals/bifpen-varimport.csv", stringsAsFactors = F)

# Flavifrons
flavcham.evaldf <- read.csv("completed-evals/flavcham-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "flavcham")
flavcham.varimpdf <- read.csv("completed-evals/flavcham-varimport.csv", stringsAsFactors = F)

flavcir.evaldf <- read.csv("completed-evals/flavcir-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "flavcir")
flavcir.varimpdf <- read.csv("completed-evals/flavcir-varimport.csv", stringsAsFactors = F)

flavlup.evaldf <- read.csv("completed-evals/flavlup-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "flavlup")
flavlup.varimpdf <- read.csv("completed-evals/flavlup-varimport.csv", stringsAsFactors = F)

flavpen.evaldf <- read.csv("completed-evals/flavpen-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "flavpen")
flavpen.varimpdf <- read.csv("completed-evals/flavpen-varimport.csv", stringsAsFactors = F)

flavrub.evaldf <- read.csv("completed-evals/flavrub-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "flavrub")
flavrub.varimpdf <- read.csv("completed-evals/flavrub-varimport.csv", stringsAsFactors = F)

# Mixtus
mixcham.evaldf <- read.csv("completed-evals/mixcham-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "mixcham")
mixcham.varimpdf <- read.csv("completed-evals/mixcham-varimport.csv", stringsAsFactors = F)

mixlup.evaldf <- read.csv("completed-evals/mixlup-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "mixlup")
mixlup.varimpdf <- read.csv("completed-evals/mixlup-varimport.csv", stringsAsFactors = F)

mixrub.evaldf <- read.csv("completed-evals/mixrub-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "mixrub")
mixrub.varimpdf <- read.csv("completed-evals/mixrub-varimport.csv", stringsAsFactors = F)

#Vosnesenskii
voscham.evaldf <- read.csv("completed-evals/voscham-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "voscham")
voscham.varimpdf <- read.csv("completed-evals/voscham-varimport.csv", stringsAsFactors = F)

voscir.evaldf <- read.csv("completed-evals/voscir-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "voscir")
voscir.varimpdf <- read.csv("completed-evals/voscir-varimport.csv", stringsAsFactors = F)

voslup.evaldf <- read.csv("completed-evals/voslup-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "voslup")
voslup.varimpdf <- read.csv("completed-evals/voslup-varimport.csv", stringsAsFactors = F)

vospen.evaldf <- read.csv("completed-evals/vospen-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "vospen")
vospen.varimpdf <- read.csv("completed-evals/vospen-varimport.csv", stringsAsFactors = F)

vosrub.evaldf <- read.csv("completed-evals/vosrub-eval.csv", stringsAsFactors = F) %>%
  mutate(X = "vosrub")
vosrub.varimpdf <- read.csv("completed-evals/vosrub-varimport.csv", stringsAsFactors = F)
```


# Create dataframe
Create a dataframe of all interaction pairings.

```{r int df}
# Make some working dataframes
all.evals <- bind_rows(bifcham.evaldf, bifcir.evaldf, biflup.evaldf, bifpen.evaldf, flavcham.evaldf, flavcir.evaldf, flavlup.evaldf, flavpen.evaldf, flavrub.evaldf, mixcham.evaldf, mixlup.evaldf, mixrub.evaldf, voscham.evaldf, voscir.evaldf, voslup.evaldf, vospen.evaldf, vosrub.evaldf)

model.types <- data.frame(model = sort(unique(all.evals$model)),
                          model_type = c("floral_predictor", "floral_predictor", "floral_predictor", "floral_predictor", "bee_predictor", "bee_predictor", "bee_predictor", "bee_predictor", "bee_predictor", "bee_predictor", "bee_predictor", "floral_predictor", "floral_predictor", "floral_predictor", "floral_predictor", "floral_predictor", "IDM", "bee_predictor", "bee_predictor", "bee_predictor", "bee_predictor", "floral_predictor", "floral_predictor", "floral_predictor", "bee_predictor", "bee_predictor", "bee_predictor", "bee_predictor", "bee_predictor", "bee_predictor", "floral_predictor", "floral_predictor", "floral_predictor", "floral_predictor", "floral_predictor"))

all.evals <- all.evals %>%
  left_join(model.types, by = "model")

int.df <- data.frame(int = NA,
                     bee_species = NA, # bifarius, flavifrons, mixtus, vosnesenskii
                     plant_genus = NA, # Chamaenerion, Cirsium, Lupinus, Penstemon, 
                     model_run = NA, # range from 1-100 for each interaction
                     delta_AUC = NA, # IDM - bbflower
                     delta_TSS = NA, # IDM - bbflower
                     delta_Boyce = NA) # IDM - bbflower

ints <- sort(unique(all.evals$X))

for(i in 1:length(ints)){
  int = ints[i]
  for(j in 1:100){
    df = all.evals %>%
      filter(X == int,
             run == j)
    delta_AUC = (df %>% filter(model_type == "IDM"))$AUC - (df %>% filter(model_type == "floral_predictor"))$AUC
    delta_TSS = (df %>% filter(model_type == "IDM"))$TSS - (df %>% filter(model_type == "floral_predictor"))$TSS
    
    temp.df = data.frame(int = int,
                         bee_species = NA,
                         plant_genus = NA,
                         model_run = j,
                         delta_AUC = delta_AUC,
                         delta_TSS = delta_TSS)
    int.df = bind_rows(int.df, temp.df)
  }
}

# Some bee and plant info
plant.info <- gbif %>%
  group_by(genus) %>%
  tally(name = "n_plant_records") %>% # number of records of this plant in GBIF
  left_join(gbif, by = "genus") %>%
  filter(!is.na(species)) %>%
  group_by(genus, n_plant_records) %>%
  summarise(n_plant_species = length(unique(species))) # number of species of this genus in GBIF

bee.info <- bbna %>%
  group_by(species) %>%
  tally(name = "n_bee_records") %>% # number of records of this bee in BBNA
  left_join(bbna, by = "species") %>%
  group_by(species, plant.host.genus, n_bee_records) %>%
  tally(name = "n_int") %>% # number of records of this interaction in PNWBBA
  mutate(relabund_int = n_int/n_bee_records) # relative abundance of this interaction among species' total

# Fill in bee and plant info
int.df <- int.df %>%
  mutate(bee_species = ifelse(str_detect(int, "^bif"), "bifarius",
                              ifelse(str_detect(int, "^flav"), "flavifrons",
                                     ifelse(str_detect(int, "^mix"), "mixtus", 
                                            "vosnesenskii"))),
         plant_genus = ifelse(str_detect(int, "cham"), "Chamaenerion", 
                              ifelse(str_detect(int, "cir"), "Cirsium",
                                     ifelse(str_detect(int, "lup"), "Lupinus",
                                            ifelse(str_detect(int, "pen"), "Penstemon",
                                                   "Rubus"))))) %>%
  left_join(plant.info, by = c("plant_genus" = "genus")) %>%
  left_join(bee.info, by = c("bee_species" = "species", "plant_genus" = "plant.host.genus"))
```

# Stats

## Absolute Model Performance

Here, we are just looking at which model is best for each of our 17 interactions.

### Bifarius
#### Chamaenerion
```{r bifcham eval plots}
# AUC
bifcham.auctest <- aov(AUC ~ model, data = bifcham.evaldf)
summary(bifcham.auctest)
TukeyHSD(bifcham.auctest)

bifcham.aucplot <- ggplot(bifcham.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("bbcham", "chambb", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.59, 1.03))
bifcham.aucplot
ggsave("figures/bifcham-auc.png", bifcham.aucplot, width = 2.5, height = 4, units = "in")

# TSS
bifcham.tsstest <- aov(TSS ~ model, data = bifcham.evaldf)
summary(bifcham.tsstest)
TukeyHSD(bifcham.tsstest)

bifcham.tssplot <- ggplot(bifcham.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("bbcham", "chambb", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.25, 1.03))
bifcham.tssplot
ggsave("figures/bifcham-tss.png", bifcham.tssplot, width = 2.5, height = 4, units = "in")
```

#### Cirsium
```{r bifcir eval plots}
# AUC
bifcir.auctest <- aov(AUC ~ model, data = bifcir.evaldf)
summary(bifcir.auctest)
TukeyHSD(bifcir.auctest)

bifcir.aucplot <- ggplot(bifcir.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("bbcir", "cirbb", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.59, 1.03))
bifcir.aucplot
ggsave("figures/bifcir-auc.png", bifcir.aucplot, width = 2.5, height = 4, units = "in")

# TSS
bifcir.tsstest <- aov(TSS ~ model, data = bifcir.evaldf)
summary(bifcir.tsstest)
TukeyHSD(bifcir.tsstest)

bifcir.tssplot <- ggplot(bifcir.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("bbcir", "cirbb", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.25, 1.03))
bifcir.tssplot
ggsave("figures/bifcir-tss.png", bifcir.tssplot, width = 2.5, height = 4, units = "in")
```
#### Lupinus

```{r biflup eval plots}
# AUC
biflup.auctest <- aov(AUC ~ model, data = biflup.evaldf)
summary(biflup.auctest)
TukeyHSD(biflup.auctest)

biflup.aucplot <- ggplot(biflup.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("bbl", "lbb", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.59, 1.03))
biflup.aucplot
ggsave("figures/biflup-auc.png", biflup.aucplot, width = 2.5, height = 4, units = "in")

# TSS
biflup.tsstest <- aov(TSS ~ model, data = biflup.evaldf)
summary(biflup.tsstest)
TukeyHSD(biflup.tsstest)

biflup.tssplot <- ggplot(biflup.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("bbl", "lbb", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.25, 1.03))
biflup.tssplot
ggsave("figures/biflup-tss.png", biflup.tssplot, width = 2.5, height = 4, units = "in")
```

#### Penstemon
```{r bifpen eval plots}
# AUC
bifpen.auctest <- aov(AUC ~ model, data = bifpen.evaldf)
summary(bifpen.auctest)
TukeyHSD(bifpen.auctest)

bifpen.aucplot <- ggplot(bifpen.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot()  +
  scale_x_discrete(limit = c("bbp", "pbb", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.59, 1.03))
bifpen.aucplot
ggsave("figures/bifpen-auc.png", bifpen.aucplot, width = 2.5, height = 4, units = "in")


# TSS
bifpen.tsstest <- aov(TSS ~ model, data = bifpen.evaldf)
summary(bifpen.tsstest)
TukeyHSD(bifpen.tsstest)

bifpen.tssplot <- ggplot(bifpen.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("bbp", "pbb", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.25, 1.03))
bifpen.tssplot
ggsave("figures/bifpen-tss.png", bifpen.tssplot, width = 2.5, height = 4, units = "in")
```

### Flavifrons
#### Chamaenerion
```{r flavcham eval plots}
# AUC
flavcham.auctest <- aov(AUC ~ model, data = flavcham.evaldf)
summary(flavcham.auctest)
TukeyHSD(flavcham.auctest)

flavcham.aucplot <- ggplot(flavcham.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("fbcham", "chambf", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.59, 1.03))
flavcham.aucplot
ggsave("figures/flavcham-auc.png", flavcham.aucplot, width = 2.5, height = 4, units = "in")

# TSS
flavcham.tsstest <- aov(TSS ~ model, data = flavcham.evaldf)
summary(flavcham.tsstest)
TukeyHSD(flavcham.tsstest)

flavcham.tssplot <- ggplot(flavcham.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("fbcham", "chambf", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.25, 1.03))
flavcham.tssplot
ggsave("figures/flavcham-tss.png", flavcham.tssplot, width = 2.5, height = 4, units = "in")
```

#### Cirsium
```{r flavcir eval plots}
# AUC
flavcir.auctest <- aov(AUC ~ model, data = flavcir.evaldf)
summary(flavcir.auctest)
TukeyHSD(flavcir.auctest)

flavcir.aucplot <- ggplot(flavcir.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("fbcir", "cirbf", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.59, 1.03))
flavcir.aucplot
ggsave("figures/flavcir-auc.png", flavcir.aucplot, width = 2.5, height = 4, units = "in")

# TSS
flavcir.tsstest <- aov(TSS ~ model, data = flavcir.evaldf)
summary(flavcir.tsstest)
TukeyHSD(flavcir.tsstest)

flavcir.tssplot <- ggplot(flavcir.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("fbcir", "cirbf", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.25, 1.03))
flavcir.tssplot
ggsave("figures/flavcir-tss.png", flavcir.tssplot, width = 2.5, height = 4, units = "in")
```

#### Lupinus
```{r flavlup eval plots}
# AUC
flavlup.auctest <- aov(AUC ~ model, data = flavlup.evaldf)
summary(flavlup.auctest)
TukeyHSD(flavlup.auctest)

flavlup.aucplot <- ggplot(flavlup.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("fbl", "lbf", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.59, 1.03))
flavlup.aucplot
ggsave("figures/flavlup-auc.png", flavlup.aucplot, width = 2.5, height = 4, units = "in")

# TSS
flavlup.tsstest <- aov(TSS ~ model, data = flavlup.evaldf)
summary(flavlup.tsstest)
TukeyHSD(flavlup.tsstest)

flavlup.tssplot <- ggplot(flavlup.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("fbl", "lbf", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.25, 1.03))
flavlup.tssplot
ggsave("figures/flavlup-tss.png", flavlup.tssplot, width = 2.5, height = 4, units = "in")
```
#### Penstemon
```{r flavpen eval plots}
# AUC
flavpen.auctest <- aov(AUC ~ model, data = flavpen.evaldf)
summary(flavpen.auctest)
TukeyHSD(flavpen.auctest)

flavpen.aucplot <- ggplot(flavpen.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("fbp", "pbf", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.59, 1.03))
flavpen.aucplot
ggsave("figures/flavpen-auc.png", flavpen.aucplot, width = 2.5, height = 4, units = "in")

# TSS
flavpen.tsstest <- aov(TSS ~ model, data = flavpen.evaldf)
summary(flavpen.tsstest)
TukeyHSD(flavpen.tsstest)

flavpen.tssplot <- ggplot(flavpen.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("fbp", "pbf", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.25, 1.03))
flavpen.tssplot
ggsave("figures/flavpen-tss.png", flavpen.tssplot, width = 2.5, height = 4, units = "in")
```

#### Rubus
```{r flavrub eval plots}
# AUC
flavrub.auctest <- aov(AUC ~ model, data = flavrub.evaldf)
summary(flavrub.auctest)
TukeyHSD(flavrub.auctest)

flavrub.aucplot <- ggplot(flavrub.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("fbrub", "rubbf", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.59, 1.03))
flavrub.aucplot
ggsave("figures/flavrub-auc.png", flavrub.aucplot, width = 2.5, height = 4, units = "in")

# TSS
flavrub.tsstest <- aov(TSS ~ model, data = flavrub.evaldf)
summary(flavrub.tsstest)
TukeyHSD(flavrub.tsstest)

flavrub.tssplot <- ggplot(flavrub.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("fbrub", "rubbf", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.25, 1.03))
flavrub.tssplot
ggsave("figures/flavrub-tss.png", flavrub.tssplot, width = 2.5, height = 4, units = "in")
```

### Mixtus
#### Chamaenerion
```{r mixcham eval plots}
# AUC
mixcham.auctest <- aov(AUC ~ model, data = mixcham.evaldf)
summary(mixcham.auctest)
TukeyHSD(mixcham.auctest)

mixcham.aucplot <- ggplot(mixcham.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("mbcham", "chambm", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.59, 1.03))
mixcham.aucplot
ggsave("figures/mixcham-auc.png", mixcham.aucplot, width = 2.5, height = 4, units = "in")

# TSS
mixcham.tsstest <- aov(TSS ~ model, data = mixcham.evaldf)
summary(mixcham.tsstest)
TukeyHSD(mixcham.tsstest)

mixcham.tssplot <- ggplot(mixcham.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("mbcham", "chambm", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.25, 1.03))
mixcham.tssplot
ggsave("figures/mixcham-tss.png", mixcham.tssplot, width = 2.5, height = 4, units = "in")
```

#### Lupinus
```{r mixlup eval plots}
# AUC
mixlup.auctest <- aov(AUC ~ model, data = mixlup.evaldf)
summary(mixlup.auctest)
TukeyHSD(mixlup.auctest)

mixlup.aucplot <- ggplot(mixlup.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("mbl", "lbm", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.59, 1.03))
mixlup.aucplot
ggsave("figures/mixlup-auc.png", mixlup.aucplot, width = 2.5, height = 4, units = "in")

# TSS
mixlup.tsstest <- aov(TSS ~ model, data = mixlup.evaldf)
summary(mixlup.tsstest)
TukeyHSD(mixlup.tsstest)

mixlup.tssplot <- ggplot(mixlup.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("mbl", "lbm", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.25, 1.03))
mixlup.tssplot
ggsave("figures/mixlup-tss.png", mixlup.tssplot, width = 2.5, height = 4, units = "in")
```

#### Rubus
```{r mixrub eval plots}
# AUC
mixrub.auctest <- aov(AUC ~ model, data = mixrub.evaldf)
summary(mixrub.auctest)
TukeyHSD(mixrub.auctest)

mixrub.aucplot <- ggplot(mixrub.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("mbrub", "rubbm", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.59, 1.03))
mixrub.aucplot
ggsave("figures/mixrub-auc.png", mixrub.aucplot, width = 2.5, height = 4, units = "in")

# TSS
mixrub.tsstest <- aov(TSS ~ model, data = mixrub.evaldf)
summary(mixrub.tsstest)
TukeyHSD(mixrub.tsstest)

mixrub.tssplot <- ggplot(mixrub.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("mbrub", "rubbm", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.25, 1.03))
mixrub.tssplot
ggsave("figures/mixrub-tss.png", mixrub.tssplot, width = 2.5, height = 4, units = "in")
```

### Vosnesenskii
#### Chamaenerion
```{r voscham eval plots}
# AUC
voscham.auctest <- aov(AUC ~ model, data = voscham.evaldf)
summary(voscham.auctest)
TukeyHSD(voscham.auctest)

voscham.aucplot <- ggplot(voscham.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("vbcham", "chambv", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.59, 1.03))
voscham.aucplot
ggsave("figures/voscham-auc.png", voscham.aucplot, width = 2.5, height = 4, units = "in")

# TSS
voscham.tsstest <- aov(TSS ~ model, data = voscham.evaldf)
summary(voscham.tsstest)
TukeyHSD(voscham.tsstest)

voscham.tssplot <- ggplot(voscham.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("vbcham", "chambv", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.25, 1.03))
voscham.tssplot
ggsave("figures/voscham-tss.png", voscham.tssplot, width = 2.5, height = 4, units = "in")
```

#### Cirsium
```{r voscir eval plots}
# AUC
voscir.auctest <- aov(AUC ~ model, data = voscir.evaldf)
summary(voscir.auctest)
TukeyHSD(voscir.auctest)

voscir.aucplot <- ggplot(voscir.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("vbcir", "cirbv", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
 theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.59, 1.03))
voscir.aucplot
ggsave("figures/voscir-auc.png", voscir.aucplot, width = 2.5, height = 4, units = "in")

# TSS
voscir.tsstest <- aov(TSS ~ model, data = voscir.evaldf)
summary(voscir.tsstest)
TukeyHSD(voscir.tsstest)

voscir.tssplot <- ggplot(voscir.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("vbcir", "cirbv", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.25, 1.03))
voscir.tssplot
ggsave("figures/voscir-tss.png", voscir.tssplot, width = 2.5, height = 4, units = "in")
```

#### Lupinus
```{r voslup eval plots}
# AUC
voslup.auctest <- aov(AUC ~ model, data = voslup.evaldf)
summary(voslup.auctest)
TukeyHSD(voslup.auctest)

voslup.aucplot <- ggplot(voslup.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("vbl", "lbv", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.59, 1.03))
voslup.aucplot
ggsave("figures/voslup-auc.png", voslup.aucplot, width = 2.5, height = 4, units = "in")

# TSS
voslup.tsstest <- aov(TSS ~ model, data = voslup.evaldf)
summary(voslup.tsstest)
TukeyHSD(voslup.tsstest)

voslup.tssplot <- ggplot(voslup.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("vbl", "lbv", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.25, 1.03))
voslup.tssplot
ggsave("figures/voslup-tss.png", voslup.tssplot, width = 2.5, height = 4, units = "in")
```

#### Penstemon
```{r vospen eval plots}
# AUC
vospen.auctest <- aov(AUC ~ model, data = vospen.evaldf)
summary(vospen.auctest)
TukeyHSD(vospen.auctest)

vospen.aucplot <- ggplot(vospen.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("vbp", "pbv", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.59, 1.03))
vospen.aucplot
ggsave("figures/vospen-auc.png", vospen.aucplot, width = 2.5, height = 4, units = "in")

# TSS
vospen.tsstest <- aov(TSS ~ model, data = vospen.evaldf)
summary(vospen.tsstest)
TukeyHSD(vospen.tsstest)

vospen.tssplot <- ggplot(vospen.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("vbp", "pbv", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.25, 1.03))
vospen.tssplot
ggsave("figures/vospen-tss.png", vospen.tssplot, width = 2.5, height = 4, units = "in")
```

#### Rubus
```{r vosrub eval plots}
# AUC
vosrub.auctest <- aov(AUC ~ model, data = vosrub.evaldf)
summary(vosrub.auctest)
TukeyHSD(vosrub.auctest)

vosrub.aucplot <- ggplot(vosrub.evaldf, aes(x = model, y = AUC)) +
  geom_boxplot() +
  scale_x_discrete(limit = c("vbr", "rbv", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.59, 1.03))
vosrub.aucplot
ggsave("figures/vosrub-auc.png", vosrub.aucplot, width = 2.5, height = 4, units = "in")

# TSS
vosrub.tsstest <- aov(TSS ~ model, data = vosrub.evaldf)
summary(vosrub.tsstest)
TukeyHSD(vosrub.tsstest)

vosrub.tssplot <- ggplot(vosrub.evaldf, aes(x = model, y = TSS)) + 
  geom_boxplot() +
  scale_x_discrete(limit = c("vbr", "rbv", "IDM"),
                   labels = c("Plant First", "Bee First", "Interaction")) +
  theme(axis.text.x = element_blank(),
        axis.title = element_blank()) +
  lims(y = c(0.25, 1.03))
vosrub.tssplot
ggsave("figures/vosrub-tss.png", vosrub.tssplot, width = 2.5, height = 4, units = "in")
```


## Relative Difference in Model Performance

Here, we want to see how we can determine whether an IDM would be better than an overlap model for a particular interaction.

*AUC*: 

```{r relative stats}
auc.test <- glmmTMB(delta_AUC ~ relabund_int + n_plant_species + n_plant_records + n_bee_records + (1|bee_species) + (1|plant_genus), data = int.df, family = gaussian)
check_collinearity(auc.test)
summary(auc.test)

tss.test <- glmmTMB(delta_TSS ~ relabund_int + n_plant_species + n_plant_records + n_bee_records + (1|bee_species) + (1|plant_genus), data = int.df, family = gaussian)
check_collinearity(tss.test)
summary(tss.test)
```

There seems to be a pretty clear story here. 